\co{Enhanced tunability in ferroelectric composites through local field enhancement and the effect of disorder}

### 2019-06-28 paper/arxiv/response_letter.tex

\documentclass[%
 aip,
 amsmath,amssymb,
%preprint,%
 reprint,%
]{revtex4-1}

\usepackage{xcolor}
\definecolor{correction}{HTML}{de5e5e}
\definecolor{reply}{HTML}{de5e5e}
\newcommand{\co}[1]{\textcolor{correction}{#1}}
\newcommand{\rep}[1]{\textcolor{reply}{{\bfseries Reply:} #1}}

@@

Overall I found the approach described by the authors to be interesting and I expect it will be useful to
 introduce this two-scale convergence method to microwave metamaterial engineering and perhaps to
  metamaterial research in higher frequency ranges as well.

In principle I think this study is publishable, but I would like to see some important clarifying revisions
 made, all are outlined below. After these revisions are adaquately addressed, I expect to be able to
  recommend publication in JAP. The authors need to address the following:

\begin{enumerate}
\item Title/Abstract/ Introduction of Paper: I think the title/abstract and overall introduction of the
 paper is somewhat misleading. These sections should be revised to make clear that the authors are
  presenting a numerical and computational study. As written, it is unclear whether the paper is presenting
   an experimental observation, or a numerical prediction.\\

\rep{It has been clarified in the abstract and introduction (lines 104-107) that this is a computational and numerical study.}

@@

\item In the introduction, please outline the actual ferroelectric composites in common use in this field.
 It is useful to know what materials this method can be used to model.

\rep{Some example and references about commonly used ferroelectric composites have been
added in the introduction (lines 32-40).}

@@

\item In the introduction: Local field engineering and field amplification has become more and more useful
 at other frequency ranges, especially in the THz and near-IR, to control the properties of other materials
  (eg. \href{https://doi.org/10.3390/photonics6010022}{Photonics 2019, 6(1), 22}). Could the authors expand
   on some other systems, besides ferro-electric metamaterials, that this method might apply to. For
    instance maybe tunable
    \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.110.217404}{GaAs meta-devices}.

    \rep{We have expanded on this point in the introduction and added possible applications of the model and corresponding references (lines 67-73).}

@@

\item In the introduction: The authors mention that there are generally limitations to the current
 numerical and theoretical models used in the field, but do not go into any detail. Could the authors
  expand on this point? What are the limitations?

  \rep{In the end of the introduction (lines 89-103), we have expanded on this point by outlining the limitations of other methods and
  the advantages of our approach in the context of this study.}

@@

\item Theory Section, A. In figure 1, are these electrostatics measurements performed by the authors? It is
 unclear based on the figure and surrounding paragraphs. I assume they are as no citation is provided for
  the data. Could the authors discuss the details of how these measurements were made? This would be useful
   for metamaterials researchers who do not work in this frequency range.

\rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A (from line 137).}

@@

  \item Theory A, last two lines "interrested" should be "interested".
\end{itemize}
\rep{Those typos and a few other ones have been corrected.}

\end{enumerate}

\section{Reviewer \#2}
\subsection{Evaluations}

\begin{itemize}
  \item Does the manuscript present original and timely results that significantly advance the knowledge in
   applied physics: Yes
  \item Does the manuscript report on convincing and rigorous data methods and analysis: Yes
  \item Is the manuscript clearly written in correct English well organized and free from ambiguities: Yes
  \item Is the title descriptive of the contents concise interesting and free of acronyms: No
  \item Does the abstract adequately and clearly describe the contents (problem approach findings) of the
   paper: Yes
  \item Are the figures in the manuscript necessary adequate well presented and clearly labelled: Yes
  \item Is the reference list appropriate: Yes

@@

  \item You gave experimental data for BST ceramics that were used to derive Landau coefficients. It is
   necessary to give some details of the sample (composition?) and measurements or to cite an experimental
    work.

    \rep{Details about the composition, fabrication and measurements of the samples at DC and microwave frequencies have been added at the beginning of Section II A  (from line 137).}

  \item You may compare the results of your simulations with the results of other studies.

  \rep{We added comparison of our results with previously published studies in section III. A (lines 261-268).}

### 2019-06-28 paper/arxiv/submit_final/manuscript.tex
optim GA ferro

\documentclass[%
 aip,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
linenumbers
]{revtex4-1}

@@

\usepackage{xcolor}
\definecolor{correction}{HTML}{de5e5e}
\newcommand{\co}[1]{\textcolor{correction}{#1}}

@@

%%%% Article title to be placed here
\title{\co{Enhanced tunability in ferroelectric composites through local field enhancement and the effect of disorder}}
\author{Benjamin Vial and Yang Hao}

%%%%%%%%% Insert author address here
\affiliation{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}

@@

This study investigates \co{numerically} the effective permittivity of composites made of
 dielectric inclusions in a ferroelectric matrix
by using a two-scale convergence method \cite{allaire_homogenization_1992,
 guenneau_homogenization_2000}.
The originality lies in the fact that a fully coupling model is employed to
calculate the electrostatic field distribution when a uniform biasing field is
applied on the structures, which will result in a local modification of the permittivity
in the ferroelectric phase due to the microstructure. As compared to a simple uncoupled model where the
ferroelectric phase is only modified through the biasing field,
the resulting effective permittivity, dielectric losses, tunability and
anisotropy significantly differ. \co{In contrast with} earlier studies in the
\co{literature} \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
the non-linear coupling beyond the first iteration and use two-scale
convergence homogenization analysis to obtain the effective parameters at
higher frequencies, instead of a capacitance-based model.
\co{The model we developed has been implemented with the finite element method (FEM)
and we realise a systematic computational study of ferroelecric-dielectric mixtures.
First, we consider} metamaterials consisting of a square array of parallel
dielectric rods with circular cross section in a ferroelectric host, and
then investigate the effect of random distribution of those rods within the unit cell.

@@

  \end{matrix}
 \right)
 \label{eq_epsftens}
\end{equation}
where each of the diagonal components have the functional form
given by \equ{eq_epsf}. Note that we will use the static values of permittivity
for the electrostatic modelling, while we are \co{interested} in the homogenized values
of permittivity at microwaves.\\
\begin{table}
 \caption{Fitting parameters to model (\ref{eq_epsf}) for the measured permittivity values as a function
  of applied electric field shown on \fig{fig1}. }
 \label{table_params_fit}
 \begin{tabular}{llll}
  \hline
  case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\ \hline
  static      & 3050       & 0.120                        & 0.024                       \\
  $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\\hline
 \end{tabular}
\end{table}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.75\textwidth]{effpar_rand_cpl.png}
 \caption{Effective parameters of the pseudo-random composites as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is taken into account.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
 \label{eff_par_2Drand_TM}
\end{figure*}
%

@@

their microstructure.

@@

\begin{figure*}[h!]
 \centering
 \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl.png}
 \caption{Effective parameters of the random 2D mixtures as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is neglected.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
 \label{eff_par_2Drand_TM_uncpl}
\end{figure*}
%
\section{Conclusion}

@@

% \bibliographystyle{RS}
\bibliography{../biblio}

>>>>

\documentclass[%
 aip,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
]{revtex4-1}

@@

%
% \usepackage{xcolor}
% \definecolor{correction}{HTML}{de5e5e}
\newcommand{\co}[1]{#1}

@@

%%%% Article title to be placed here
\title{\co{Enhanced tunability in ferroelectric composites through local field enhancement and the effect of disorder}}
\author{Benjamin Vial}
\email{b.vial@qmul.ac.uk}
\author{Yang Hao}
\email{y.hao@qmul.ac.uk}

%%%%%%%%% Insert author address here
\affiliation{School of Engineering and Computer Science, Queen Mary, University of London, London, E1 4NS, United Kingdom}
\date{\today}

@@

This study investigates \co{numerically} the effective permittivity of composites made of
 dielectric inclusions in a ferroelectric matrix
by using a two-scale convergence method \cite{allaire_homogenization_1992,
 guenneau_homogenization_2000}.
The originality lies in the fact that a fully coupling model is employed to
calculate the electrostatic field distribution when a uniform biasing field is
applied on the structures, which will result in a local modification of the permittivity
in the ferroelectric phase due to the microstructure. As compared to a simple uncoupled model where the
ferroelectric phase is only modified through the biasing field,
the resulting effective permittivity, dielectric losses, tunability and
anisotropy significantly differ. \co{In contrast with} earlier studies in the
\co{literature} \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for
the non-linear coupling beyond the first iteration and use two-scale
convergence homogenization analysis to obtain the effective parameters at
higher frequencies, instead of a capacitance-based model \co{valid in the static regime.
This is an important point, as contrarily to most homogenization procedures that are based on a
quasi-static approximation, the two scale convergence method fixes the frequency and lets the characteristic
size of the system (the periodicity of the composites) tend to zero \cite{guenneau_homogenization_2000}. This asymptotic analysis allows one to study the frequency dependence of the effective parameters.
In addition, analytical models for the effective permittivity routinely employed in the literature
such as Maxwell-Garnett or Bruggeman theories are limited to a few canonical shapes of the inclusions, and
cannot handle arbitrary geometries and media with spatially varying properties. This last point is
of particular importance in the context of this study since we have to account for the field induced local permittivity change.}\\
\co{The model we developed has been implemented with the finite element method (FEM)
and we realise a systematic computational study of ferroelecric-dielectric mixtures.
First, we consider} metamaterials consisting of a square array of parallel
dielectric rods with circular cross section in a ferroelectric host, and
then investigate the effect of random distribution of those rods within the unit cell.

@@

  \end{matrix}
 \right)
 \label{eq_epsftens}
\end{equation}
where each of the diagonal components have the functional form
given by \equ{eq_epsf}. Note that we will use the static values of permittivity
for the electrostatic modelling, while we are \co{interested} in the homogenized values
of permittivity at microwaves.\\
\begin{table}
 \caption{Fitting parameters to model (\ref{eq_epsf}) for the measured permittivity values as a function
  of applied electric field shown on \fig{fig1}. }
 \label{table_params_fit}
 \begin{ruledtabular}
 \begin{tabular}{llll}
  case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\
  \hline
  static      & 3050       & 0.120                        & 0.024                       \\
  $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\
 \end{tabular}
 \end{ruledtabular}
\end{table}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.75\textwidth]{effpar_rand_cpl}
 \caption{Effective parameters of the pseudo-random composites as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is taken into account.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
 \label{eff_par_2Drand_TM}
\end{figure*}
%

@@

their microstructure. \co{Those observations are consistent with previously published numerical and experimental results \cite{padurariu_tailoring_2012}
 where the local field enhancement in porous ferroelectrics has been shown to possibly increase tunability with reducing permittivity for small porosity levels. Our appraoch also agrees with an analytical spherical inclusion model predicting an increase of the tunability with the dilution of the ferroelectric \cite{sherman_ferroelectric-dielectric_2006}.}\\

@@

\begin{figure*}[h!]
 \centering
 \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl}
 \caption{Effective parameters of the random 2D mixtures as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is neglected.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
 \label{eff_par_2Drand_TM_uncpl}
\end{figure*}
%
\section{Conclusion}

@@

% \bibliographystyle{RS}
\bibliography{biblio}
